\texttt{Anon}Dataset: A collection of benchmark datasets for learning with graphs

### 2020-06-08 main.tex
MC.
New exp. for Yeast (replaces TRIANGLES)

\paragraph{Present work.} 
Here, we give an overview of \textsc{\texttt{Anon}}. The benchmark collection consists of over 120 datasets from a wide range of domains for supervised learning with graphs, i.e., classification and regression. All datasets are provided in a standard dataset format at \url{Anon} and are easily accessible from popular graph learning frameworks such as \textsc{Pytorch Geometric}~\cite{Fey+2019} and \textsc{DGL}~\cite{Wan+2019}. To facilitate standard comparison of kernel and neural approaches, we provide implementations of standard algorithms and easy-to-use evaluation procedures. Moreover, we report results on an experimental study comparing graph kernels and GNNs on a subset of the \textsc{\texttt{Anon}}.

@@

The papers~\cite{Fey+2019,Che+2019,Err+2019,Dwi+2020} evaluate GNNs using a unified evaluation procedure, however, they only use small- or medium scale datasets. Recently, \url{ogb.stanford.edu}~\cite{Hu+2020} launched, however, the provided datasets for graph classification focus on chemistry and bioinformatic applications, and the number is quite limited at this point. Moreover, the datasets proposed in~\cite{Fer+2019} focuses on instances from planning competitions. http://www.jmlr.org/papers/volume21/18-370/18-370.pdf

@@

			\multirow{4}{*}{\rotatebox{90}{Kernel}}	& \text{1-WL}  &   $52.3$ \scriptsize $\pm 0.7 \pm 6.7 $       & $72.6$ \scriptsize $\pm  0.6 \pm 4.1$ &  $50.3$ \scriptsize $\pm 0.8 \pm  3.8 $ & $84.5$ \scriptsize $\pm 0.3 \pm 1.7$ & $72.8$ \scriptsize $\pm 0.8 \pm  3.9 $ & $73.9$ \scriptsize $\pm 0.6 \pm 3.2$  \\
			%				& \text{2-LWL} &   \scriptsize $\pm \pm $       &  \scriptsize $\pm \pm $ &  \scriptsize $\pm  \pm  $ & \scriptsize $\pm   \pm $ &  \scriptsize $\pm \pm $ &  \scriptsize $\pm  \pm  $   \\
			%				& \text{2-LWL$^+$} &   \scriptsize $\pm \pm $       &  \scriptsize $\pm \pm $ &  \scriptsize $\pm  \pm  $ & \scriptsize $\pm   \pm $ &  \scriptsize $\pm \pm $ &  \scriptsize $\pm  \pm  $   \\
			& \text{WLOA} & $58.4$ \scriptsize $\pm 2.0 \pm 7.4$       &  $73.2$ \scriptsize $\pm 0.8 \pm 3.8$ & $49.4$ \scriptsize $\pm 0.3 \pm 3.6 $ & $85.4$ \scriptsize $\pm  0.2 \pm 1.4$ & $73.2$ \scriptsize $\pm 0.6 \pm 3.5$ & $88.4$ \scriptsize $\pm 0.4 \pm 2.1 $   \\
			& \text{GR}            &    $30.1$ \scriptsize $\pm 0.8 \pm 6.0$       & $59.0$ \scriptsize $\pm 0.9 \pm 5.7$ & $39.6$ \scriptsize $\pm 0.5 \pm 3.6  $ & $66.2$ \scriptsize $\pm 0.2\pm 2.2$ & $71.4$ \scriptsize $\pm 0.6\pm 4.4 $ & $60.0$ \scriptsize $\pm 0.2 \pm  2.7$   \\
			& \text{SP}            & $40.5$  \scriptsize $\pm 1.6 \pm 6.2$       & $58.7$ \scriptsize $\pm 0.9 \pm 4.6 $ & $39.5$ \scriptsize $\pm 0.9 \pm 4.2$ & $74.5$ \scriptsize $\pm 0.4\pm 2.2 $  &$75.9$ \scriptsize $\pm 0.6 \pm 4.0$ & $84.6$ \scriptsize $\pm0.2\pm 0.4 $  \\
			\cmidrule{2-8}	
			\multirow{2}{*}{\rotatebox{90}{GNN}}	& \textsc{Gin-$\varepsilon$}   &   \scriptsize $\pm \pm $       & $72.4$ \scriptsize $\pm 0.6\pm 4.0 $ &  $49.7$ \scriptsize $\pm 0.2 \pm  3.9$ & $79.0$ \scriptsize $\pm  0.5 \pm 1.9 $ &  $71.3$ \scriptsize $\pm 0.4 \pm 4.0$ & $90.0$ \scriptsize $\pm 0.6 \pm 1.7 $   \\
			& \textsc{Gin-$\varepsilon$-JK} &     \scriptsize $\pm \pm $       & $73.4$ \scriptsize $\pm 0.6\pm 4.4$ & $50.6$ \scriptsize $\pm 0.5 \pm 4.2 $ & $79.1$ \scriptsize $\pm  0.2 \pm 1.5 $ & $72.4$ \scriptsize $\pm 0.6 \pm 1.7 $ & $90.6$ \scriptsize $\pm 0.2 \pm  2.2$   \\
			\bottomrule
	\end{tabular}}
\end{table*}		
\begin{table*}[t]\centering		
	\caption{Classification accuracies in percent and standard deviations on mid-scale datasets.}
	\label{t2ll}	
	\resizebox{0.75\textwidth}{!}{ 	\renewcommand{\arraystretch}{1.1}
		\begin{tabular}{@{}c <{\enspace}@{}lccccc@{}}	\toprule
			& \multirow{3}{*}{\vspace*{4pt}\textbf{Method}}&\multicolumn{5}{c}{\textbf{Dataset}}\\\cmidrule{3-7}
			& & {\textsc{Mcf-7}}         &  {\textsc{Molt-4}}      & {\textsc{Yeast}}           & {\textsc{github\_star.}}       & {\textsc{reddit\_threads}}      \\	\toprule
			\multirow{3}{*}{\rotatebox{90}{Kernel}}	& \text{1-WL}    & 
			$94.5$ \scriptsize $<0.1 \pm 0.4$  &$94.6$ \scriptsize $\pm 0.1  \pm 0.3$ & $89.2$ \scriptsize $\pm 0.1 \pm 0.4$ &  $63.9$ \scriptsize $\pm 0.1\pm 1.3$ &$77.0$ \scriptsize $<0.1 \pm 0.3$  \\

>>>>

\xhdr{Present work.} 
Here, we give an overview of \textsc{\texttt{Anon}}. The benchmark collection consists of over 120 datasets from a wide range of domains for supervised learning with graphs, i.e., classification and regression. All datasets are provided in a standard dataset format at \url{Anon} and are easily accessible from popular graph learning frameworks such as \textsc{Pytorch Geometric}~\cite{Fey+2019} and \textsc{DGL}~\cite{Wan+2019}. To facilitate standard comparison of kernel and neural approaches, we provide implementations of standard algorithms and easy-to-use evaluation procedures. Moreover, we report results on an experimental study comparing graph kernels and GNNs on a subset of the \textsc{\texttt{Anon}}.

@@

The papers~\cite{Fey+2019,Che+2019new,Err+2019,Dwi+2020} evaluate GNNs using a unified evaluation procedure, however, they only use small- or medium scale datasets. Recently, \url{ogb.stanford.edu}~\cite{Hu+2020} launched, however, the provided datasets for graph classification focus on chemistry and bioinformatic applications, and the number is quite limited at this point. Moreover, the datasets proposed in~\cite{Fer+2019} focuses on instances from planning competitions. http://www.jmlr.org/papers/volume21/18-370/18-370.pdf

@@

			\multirow{4}{*}{\rotatebox{90}{Kernel}}	& \text{1-WL}  &   $52.3$ \scriptsize $\pm 0.7 \pm 6.7 $       & $72.6$ \scriptsize $\pm  0.6 \pm 4.1$ &  $50.3$ \scriptsize $\pm 0.8 \pm  3.8 $ & $84.5$ \scriptsize $\pm 0.3 \pm 1.7$ & $72.8$ \scriptsize $\pm 0.8 \pm  3.9 $ & $73.9$ \scriptsize $\pm 0.6 \pm 3.2$  \\
			%				& \text{2-LWL} &   \scriptsize $\pm \pm $       &  \scriptsize $\pm \pm $ &  \scriptsize $\pm  \pm  $ & \scriptsize $\pm   \pm $ &  \scriptsize $\pm \pm $ &  \scriptsize $\pm  \pm  $   \\
			%				& \text{2-LWL$^+$} &   \scriptsize $\pm \pm $       &  \scriptsize $\pm \pm $ &  \scriptsize $\pm  \pm  $ & \scriptsize $\pm   \pm $ &  \scriptsize $\pm \pm $ &  \scriptsize $\pm  \pm  $   \\
			& \text{WLOA} & $58.4$ \scriptsize $\pm 2.0 \pm 7.4$       &  $73.2$ \scriptsize $\pm 0.8 \pm 3.8$ & $49.4$ \scriptsize $\pm 0.3 \pm 3.6 $ & $85.4$ \scriptsize $\pm  0.2 \pm 1.4$ & $73.2$ \scriptsize $\pm 0.6 \pm 3.5$ & $88.4$ \scriptsize $\pm 0.4 \pm 2.1 $   \\
			& \text{GR}            &    $30.1$ \scriptsize $\pm 0.8 \pm 6.0$       & $59.0$ \scriptsize $\pm 0.9 \pm 5.7$ & $39.6$ \scriptsize $\pm 0.5 \pm 3.6  $ & $66.2$ \scriptsize $\pm 0.2\pm 2.2$ & $71.4$ \scriptsize $\pm 0.6\pm 4.4 $ & $60.0$ \scriptsize $\pm 0.2 \pm  2.7$   \\
			& \text{SP}            & $40.5$  \scriptsize $\pm 1.6 \pm 6.2$       & $58.7$ \scriptsize $\pm 0.9 \pm 4.6 $ & $39.5$ \scriptsize $\pm 0.9 \pm 4.2$ & $74.5$ \scriptsize $\pm 0.4\pm 2.2 $  &$75.9$ \scriptsize $\pm 0.6 \pm 4.0$ & $84.6$ \scriptsize $\pm0.2\pm 0.4 $  \\
			\cmidrule{2-8}	
			\multirow{2}{*}{\rotatebox{90}{GNN}}	& \textsc{Gin-$\varepsilon$}   &  39.5 \scriptsize $\pm 1.4 \pm 7.6 $       & $72.4$ \scriptsize $\pm 0.6\pm 4.0 $ &  $49.7$ \scriptsize $\pm 0.2 \pm  3.9$ & $79.0$ \scriptsize $\pm  0.5 \pm 1.9 $ &  $71.3$ \scriptsize $\pm 0.4 \pm 4.0$ & $90.0$ \scriptsize $\pm 0.6 \pm 1.7 $   \\
			& \textsc{Gin-$\varepsilon$-JK} &  d   \scriptsize $\pm \pm $       & $73.4$ \scriptsize $\pm 0.6\pm 4.4$ & $50.6$ \scriptsize $\pm 0.5 \pm 4.2 $ & $79.1$ \scriptsize $\pm  0.2 \pm 1.5 $ & $72.4$ \scriptsize $\pm 0.6 \pm 1.7 $ & $90.6$ \scriptsize $\pm 0.2 \pm  2.2$   \\
			\bottomrule
	\end{tabular}}
\end{table*}		
\begin{table*}[t]\centering		
	\caption{Classification accuracies in percent and standard deviations on mid-scale datasets.}
	\label{t2ll}	
	\resizebox{0.75\textwidth}{!}{ 	\renewcommand{\arraystretch}{1.1}
		\begin{tabular}{@{}c <{\enspace}@{}lccccc@{}}	\toprule
			& \multirow{3}{*}{\vspace*{4pt}\textbf{Method}}&\multicolumn{5}{c}{\textbf{Dataset}}\\\cmidrule{3-7}
			& & {\textsc{Mcf-7}}         &  {\textsc{Molt-4}}      & {\textsc{Yeast}}           & {\textsc{github\_star.}}       & {\textsc{reddit\_threads}}      \\	\toprule
			\multirow{3}{*}{\rotatebox{90}{Kernel}}	& \text{1-WL}    & 
			$94.5$ \scriptsize $<0.1 \pm 0.4$  &$94.6$ \scriptsize $\pm 0.1  \pm 0.3$ & $89.2$ \scriptsize $\pm 0.1 \pm 0.4$ &  $63.9$ \scriptsize $\pm 0.1\pm 1.3$ &$77.0$ \scriptsize $<0.1 \pm 0.3$  \\
